---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# creature

<!-- badges: start -->
<!-- badges: end -->

The goal of the package is to create a creature that will accompany you when you feel lonely. You will find it at the bottom of your Rmd document or Shiny app. The creature was initially developed by [Justin Windle](https://soulwire.github.io/sketch.js/), I've just found it cool and adapted it to R. You can say this is an R wrapper. 



## Installation


You can install the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}

# install.packages("remotes")

remotes::install_github("feddelegrand7/creature")


```


## Example

A demo is available [here](https://ihaddadenfodil.com/post/introducing-the-creature-package-interactive-animations-in-rmd-documents-and-shiny-apps/)


## Code of Conduct

Please note that the creature project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
